---
output:
  pdf_document: default
  html_document:
    df_print: paged
---
\fontfamily{cmr}
\fontsize{10}{8}
\fontseries{b}
\vspace{0.1cm}
\selectfont
```{r,echo = FALSE,comment=NA }
library('tinytex')
library("kableExtra")
library("xtable")
if (toreturnall$whoismature[i] == "3p is Mature") {
  miRNA3p <- paste0(" ", as.character(ToReport$mature[i]))
  miRNA5p <- paste0("* ", as.character(ToReport$star[i]))
} else {
    miRNA5p <- paste0(" ",as.character(ToReport$mature[i]))
    miRNA3p <- paste0("* ", as.character(ToReport$star[i]))
}
```
`>``r as.character(ToReport[i,"UserName"])` (`r as.character(ToReport[i,"UserName"])`)

`r as.character(toreturnall$precursor[i])`

`>``r as.character(ToReport[1,"UserName"])`_3p`r as.character(miRNA3p)`

`>``r as.character(ToReport[1,"UserName"])`_5p`r as.character(miRNA5p)`

Genomic coordinates: `r as.character(toreturnall[toprintaligns$ID ==  ToReport[i,"Name"],]$Loci)`
Final score: `r as.character(toreturnall[toprintaligns$ID ==  ToReport[i,"Name"],]$Score)`
```{r,echo = FALSE,comment=NA }
alignmentResult <- as.data.frame(as.character(Alignmentlist[[i]]))
colnames(alignmentResult) <-NULL
print(alignmentResult)
```
```{r,echo = FALSE,comment=NA }
library("jpeg")
im <- readJPEG(paste0('./www/images/', ToReport[i,"Name"], "_fold.jpg"))
plot (0:1, 0:1, type = "n", ann = FALSE, axes = FALSE)
rasterImage (im, -0.5, 0, 1, 2)
```

```{r,echo = FALSE,comment=NA }
library("png")
png <- readPNG(paste0('./www/plots/', ToReport[i,"Name"], ".png"))
plot.new()
rasterImage(png, 0, 0, 1, 1)
```
